---
title: "A tour of IsoformVisRNA"
author: Nayeon Hyun
date: "`r format(Sys.time(), '%d %b %Y')`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: false
vignette: >
  %\VignetteIndexEntry{Introduction_IsoformVisRNA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(IsoformVisRNA)
```

## Introduction

`IsoformVisRNA` is an R Package that generates plots to compare transcript-level expression counts. 
It takes normalized count matrices generated by kallisto and its corresponding metadata for its analysis.
This package have functions to generate figures like box plots and bar plots to compare the expression ratios of various transcripts in a gene.
This package will improve the workflow in the analysis a gene’s alternative splicing and help determine the dominant splicing pattern in samples.
The `IsoformVisRNA` package was developed using `R version 4.3.1 (2023-06-16)`, `Platform: x86_64-apple-darwin20 (64-bit)` and `Running under: macOS Monterey 12.3.1`. See `help(package = "TestingPackage")` for further details. 

To download **IsoformVisRNA**, use the following commands:

``` r
require("devtools")
devtools::install_github("hyunnaye/IsoformVisRNA", build_vignettes = TRUE)
library("IsoformVisRNA")
```
To list all sample functions available in the package:
``` r
ls("package:IsoformVisRNA")
```

To list all sample datasets available in the package:
``` r
data(package = "IsoformVisRNA")
```

<br>


### Minimal requirements

* You will need to generate transcript-level count matrices in tsv format using kallisto.

### Other

## Applications

*combineCounts* combines all kallisto count matrices to a single data frame.
To get more information about *combineCounts* function, the help documentation will helpful:
```{r, }
library(IsoformVisRNA)
?IsoformVisRNA::combineCounts
``` 

*calculateRatios* function generates expression ratios for 2 given transcript ids for all samples.
To get more information about *calculateRatios* function, view the help documentation:
```{r, }
library(IsoformVisRNA)
?IsoformVisRNA::calculateRatios
``` 

To create plots like bar plots and box plots to compare your desired expression ratios, you can use *generateBarPlot* and *generateBoxPlot*.
```{r, }
library(IsoformVisRNA)
?IsoformVisRNA::generateBarPlot
``` 

```{r, }
library(IsoformVisRNA)
?IsoformVisRNA::generateBoxPlot
``` 

## Package References

- Hyun, N. (2023) IsoformVisRNA: Isoform Visualizer for RNA-seq. 
  Unpublished. https://github.com/hyunnaye/IsoformVisRNA

<br>

## Other References

  ENCODE Project Consortium.. An integrated encyclopedia of DNA elements in the human genome. Nature 2012 Sep       
  6;489(7414):57-74. PMID: 22955616
  
  H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.
  
  Kassambara A (2023). _ggpubr: 'ggplot2' Based Publication Ready Plots_. R package version 0.6.0,
  <https://CRAN.R-project.org/package=ggpubr>.
  
  R Core Team (2023). _R: A Language and Environment for Statistical Computing_. R Foundation for Statistical
  Computing, Vienna, Austria. <https://www.R-project.org/>.
  
  Wickham H (2022). _stringr: Simple, Consistent Wrappers for Common String Operations_. R package version
  1.5.0, <https://CRAN.R-project.org/package=stringr>.
  
  Wickham H, François R, Henry L, Müller K, Vaughan D (2023). _dplyr: A Grammar of Data Manipulation_. R
  package version 1.1.3, <https://CRAN.R-project.org/package=dplyr>.
  
----

```{r}
sessionInfo()
```
